\newpage
\thispagestyle{empty}

\chapter{Specifications}

\section{People definition}

This project goal is to target community of gamer, to provide a 2D game with a long life time thanks to the map editor. By making custom maps, people will be able to play as long as their imagination let them create maps.

To make sure that the created maps are fun to play, we want that the solution be used by people loving 2D games, so they have enough experience to make nice custom maps.

\section{Pain points}

A recurent problem in editing software is difficulty to use it. So for our software we will make a major point to develop a software easy to use. We want our software usable at the first sight.

Gamers have no time to practice or learn for developpment skills, that's why we want that the editor can be use without seeing programming language, only use with graphic interface in a drag and drog software type.

\newpage
\section{Scenarios}

\subsection{Using EditKong from scratch}

\begin{itemize}
\item Create a new map
\subitem Define map name 
\subitem Define map size
\item Draw your map
\subitem Drag and drop blocks
\subitem Insert logic in blocks
\item Place your objective
\subitem Define the start point
\subitem Define the end point
\subitem Define the target point
\item Save you map
\item Start playing
\end{itemize}

\subsection{Using EditKong from existing map}

\section{Goals / Non Goals}
\section{Priority}
For this project, we are going to start by making the editor, and we will finish by making the game example. Indeed, the game is an example, not the finality.
\section{MileStone}
